### 2020-01-09 Article.tex
Pequeño update

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is

>>>>

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. A labeled copy
of $H$ in $G$ is a sub-hypergraph $H_2\subseteq G$ together with
an isomorphism $f$ from $H$ to $H_2$. Clearly, the number
of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
of copies of $H$ in $G$.
